---
title: "Using R to Scrape Website Text, pt 1"
author: "John Yuill"
date: "October 1, 2016"
output: html_document
---

```{r, global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)


```

### Scraping Web Pages to Extract Text for Analysis

Basic demonstration of how to scrape web pages for text analysis.
* Includes example of counting images

* Using rvest package
    + note that XML package also has to be installed
    
```{r}
library(rvest)
library(dplyr)


```

#### Process

1. Select URL and set as a variable
2. Use rvest's 'read_html' function to scrape the page and store it in a variable
3. Use Chrome plugin [Selector Gadget](https://chrome.google.com/webstore/detail/selectorgadget/mhjhnkcfbdhnjickkkdbjoemdmbfginb?hl=en) to identify relevant CSS selector for target content
4. Extract the CSS selector from page data using html_node(s) (singular if first node, plural if all)
5. Remove html tags using html_text
    + Generates character vector with each node as an item
6. Remove any extraneous text items - standard footers, etc
    + Use standard susetting techniques
7. Collapse all the items in the list into a single paragraph

#### Getting text from article
```{r}
pgurl <- "https://www.needforspeed.com/news/fiveways"
htmlpg <- read_html(pgurl)
cssnode <- "p" 
article <- html_nodes(htmlpg,cssnode)
articletext <- html_text(article)
articletext <- articletext[1:(length(articletext)-3)]

articlesingle <- paste(articletext, collapse=" ")
#articleframe <- data.frame(articletext)


```

* Page: `r pgurl`
* Css selector: `r cssnode`

```{r}
articlesingle
```

Word count
```{r}
# count words in article
wordcount <- sapply(gregexpr("[[:alpha:]]+", articlesingle), function(x) sum(x > 0))
```
* word count: `r wordcount`


#### Counting Images on page
```{r}
#pgurl <- "https://www.needforspeed.com/news/deluxe-edition"
pgurl <- "https://www.needforspeed.com/news/the-icons"
htmlpg <- read_html(pgurl)
cssnode <- ".article_body img" 
image <- html_nodes(htmlpg,cssnode)
imgnum <- length(image)

```
* Page: `r pgurl`
* CSS selector: `r cssnode`
* No. of images: `r imgnum`


#### References

* [rvest Easy Scraping with R](https://blog.rstudio.org/2014/11/24/rvest-easy-web-scraping-with-r/)
* [Webscraping with R and rvest (video)](http://www.computerworld.com/article/2909560/business-intelligence/web-scraping-with-r-and-rvest-includes-video-code.html)
* [Count the Number of Words in a String in R](http://stackoverflow.com/questions/8920145/count-the-number-of-words-in-a-string-in-r)
* [R Code: Reading, Preprocessing, Counting Text](http://www.katrinerk.com/courses/words-in-a-haystack-an-introductory-statistics-course/schedule-words-in-a-haystack/r-code-the-text-mining-package) - not used here but potentially good reference for more sophisticated processing/analysis 
